
---
title: "OME Ashton DDD comparision"
author:  "Mofi Islam and Dennis Wollersheim "
date: "2019-12-19"
output:
workflowr::wflow_html:
toc: false
---

```{r pre_initial, echo=FALSE, results='hide', message=FALSE, warning=FALSE}

rm(list=ls())
options(width = 200)
show_code = FALSE
#pts_chunk$set(echo = FALSE)

```


```{r initial, echo=FALSE, results='hide', message=FALSE, warning=FALSE}


source('lib/functions.R')
source('lib/get_data.R')
library(kableExtra)
library(readxl)


 
source('lib/functions.R')
source('lib/get_data.R')

library(readxl)

df_oral=tibble( pbs_route=c('TABLET','ORAL LIQUID or SACH', 'LOZENGE','CAPSULE','SACHET'))

my_dbReadTable('continuing.item') %>%
  mutate( drug = str_replace( generic_name, ' .*','')) %>% 
  { . } -> df_item 

df_item %>% 
  filter( type_code != 10 ) %>%
  arrange(drug) %>%
  { . } -> df_item_ome

read_excel( 'data/OME_input.xls') %>% 
  { . } ->    df_ome 

df_ome %>%
  filter( pbs_route=="ORAL") %>%
  select( -pbs_route ) %>%
  crossing( df_oral ) %>%
  bind_rows( df_ome  %>% filter( pbs_route!="ORAL") ) %>% 
  { . } -> df_ome_enhanced

df_item_ome %>% 
  left_join( df_ome_enhanced %>% select( type_code, pbs_route, ome_mg_factor), by=c('type_code', 'pbs_route')) %>% 
  mutate(ashton_mg_factor = NA) %>%
  { . } -> df_item_ome_final


################################################################################
# Ashton
################################################################################

read_csv( 'data/ashton_input.csv') %>% 
  janitor::clean_names() %>%
  { . } ->    df_ashton_input

df_item %>% 
  filter( type_code == 10 ) %>%
  arrange(drug) %>%
  { . } -> df_item_ashton 

# error check, makes sure we get everything
df_item_ashton %>%
  anti_join( df_ashton_input)

df_item_ashton %>%
  inner_join( df_ashton_input) %>% 
  mutate(ome_mg_factor = NA) %>%
  { . } -> df_item_ashton





```

# DDD OME equivalence testing

OME does not correspond with DDD.  It acts much closer to the inverse of DDD.  Below is a table, demonstating that.  For each drug and route combination, the ddd:ome ratio is much more variable, where as the ddd:(1/ome) ratio is much more consistent

```{r check_ome, echo=FALSE}

df_item_ome %>% 
  left_join( df_ome_enhanced %>% select( type_code, pbs_route, ome_mg_factor), by=c('type_code', 'pbs_route')) %>%
  filter( !is.na(ome_mg_factor )) %>%
  mutate( pbs_route = ifelse( pbs_route %in% df_oral$pbs_route, 'ORAL', pbs_route)) %>%
  distinct( drug, pbs_route, ddd_mg_factor, ome_mg_factor ) %>%
  mutate( inverse_ome_mg_factor = 1/ome_mg_factor,
         ddd_ome_ratio = ddd_mg_factor / ome_mg_factor,
         ddd_inverse_ome_ratio = ddd_mg_factor / inverse_ome_mg_factor
         )  %>% 
  set_names( ~ str_replace( ., '_mg_factor', '')) %>%
  mutate_if(is.numeric, round,2) %>%
  kable(padding=30) %>%
  kableExtra::kable_styling()

```


# DDD Ashton equivalence testing

On the other hand, the ashton factor /does/ act more like ddd. Below is a table showing, for each drug and route combination, the ddd:ashton ratio, and the ddd:inverse ashton ratio.  The ddd:ashton ratio is consistent, implying that it should be in the denominator


```{r check_ashton, echo=FALSE}

df_item_ashton %>%
  distinct( drug, ashton_mg_factor, ddd_mg_factor) %>%
  mutate( inverse_ashton_mg_factor = 1/ashton_mg_factor,
        ddd_ashton_ratio = ddd_mg_factor / ashton_mg_factor,
        ddd_inverse_ashton_ratio = ddd_mg_factor / inverse_ashton_mg_factor ) %>% 
  set_names( ~ str_replace( ., '_mg_factor', '')) %>%
  mutate_if(is.numeric, round,2) %>%
  kable(padding=10L, digits=2) %>%
  kableExtra::kable_styling()


```
